SEER Medicaid

### 2023-10-03 Manuscript Analysis code 0 to 19.Rmd
Updated using ghlt contrast furnction for time interval calculations

# Run models based on intervals for Medicaid_flag
```{r}
# first interval
seer0to19first<-seer0to19.cp.format[which(seer0to19.cp.format$interval=="First"),]
# adjusted models 0 to 19
res.cox12 <- coxph(Surv(fumo, can_dead) ~ In_Medicaid_Flag + race_ethnicity +age_cat + 
                     Yost_ACS_2006_2010_quintile + cluster(state), data = seer0to19first) 
res.cox12
summary(res.cox12)

# second interval
seer0to19second<-seer0to19.cp.format[which(seer0to19.cp.format$interval=="Second"),]
# adjusted models 0 to 19
res.cox24 <- coxph(Surv(fumo, can_dead) ~ In_Medicaid_Flag + race_ethnicity +age_cat + 
                     Yost_ACS_2006_2010_quintile + cluster(state), data = seer0to19second) 
res.cox24
summary(res.cox24)

# third interval
seer0to19third<-seer0to19.cp.format[which(seer0to19.cp.format$interval=="Third"),]

# adjusted models 0 to 19
res.cox36 <- coxph(Surv(fumo, can_dead) ~ In_Medicaid_Flag + race_ethnicity +age_cat + 
                     Yost_ACS_2006_2010_quintile + cluster(state), data = seer0to19third) 
res.cox36
summary(res.cox36)

# fourth interval
seer0to19fourth<-seer0to19.cp.format[which(seer0to19.cp.format$interval=="Fourth"),]
# adjusted models 0 to 19
res.cox36plus <- coxph(Surv(fumo, can_dead) ~ In_Medicaid_Flag + race_ethnicity +age_cat + 
                     Yost_ACS_2006_2010_quintile + cluster(state), data = seer0to19fourth) 
res.cox36plus
summary(res.cox36plus)

@@

# SUPPLEMENTARY TABLE 6a and Graph hazard ratios and confidence intervals across time for Medicaid_flag variable
```{r}
# need to get HRs in a dataframe
a<-as.data.frame(exp(cbind(HR = coef(res.cox12), confint(res.cox12))))
   a<-a[c(1),] %>%
    rownames_to_column() %>%
    mutate(model= 0) %>%
     mutate(Group = "Overall")

b<-as.data.frame(exp(cbind(HR = coef(res.cox24), confint(res.cox24))))
   b<-b[c(1),] %>%
    rownames_to_column() %>%
    mutate(model= 1) %>%
     mutate(Group = "Overall")

c<-as.data.frame(exp(cbind(HR = coef(res.cox36), confint(res.cox36))))
   c<-c[c(1),] %>%
    rownames_to_column() %>%
    mutate(model= 2) %>%
     mutate(Group = "Overall")

d <-as.data.frame(exp(cbind(HR = coef(res.cox36plus), confint(res.cox36plus))))
   d<-d[c(1),] %>%
    rownames_to_column() %>%
    mutate(model=3) %>%
     mutate(Group = "Overall")

SuppTable6a <- rbind(a,b,c,d)

SuppTable6a$model <- factor(SuppTable6a$model, levels = c(0:3), labels = c("0 to 12 months", "12 to 24 months","24 to 36 months", ">36 months"))

# graph HRs and 95% CIs
SuppTable6a %>%
  ggplot() +
  geom_point(aes(y=HR, x=model)) + 
  #scale_color_manual(values=c("black", "blue", "green", "red"), name="") + 
  geom_hline(yintercept =1, linetype=2) +
  theme(axis.text.y=element_blank()) +
  geom_errorbar(aes(y=HR, x=model, ymax = `2.5 %`, ymin = `97.5 %`), width = 0.1) +
  theme_bw() +
  theme(axis.line = element_line(colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank(),
    axis.text.x=element_text(size=11, face = "bold", color = "black"),
    axis.text.y=element_text(size=11, face = "bold", color = "black"),
    axis.title.x=element_text(size=12, face = "bold", color = "black"),
    axis.title.y=element_text(size=12, face = "bold", color = "black"))+
  coord_flip() 
```

# SUPPLEMENTARY TABLE 6b: Which cancer is driving this? 
```{r}
# Split a survival data set at specified times to form a counting process format
# For those with survival time of 0, add 0.5 mo because otherwise splitting doesn't work and it is more accurate

cantype <- function(cantype, int, time){

df <- survSplit(data  = seer0to19 %>% 
                  filter(can_type == cantype),
                            cut   = c(12, 24, 36),       # cut at time 12,24,36
                            end   = "fumo_half",    # original survival time
                            event = "can_dead",   # event indicator
                            start = "start")    # will be created. zero by default

# Recoding
df <- within(df, {
    # Create new survival object
    SurvObj <- Surv(start, fumo_half, can_dead) 
    # Create interval indicator
    interval <- factor(start, levels = c(0,12, 24, 36), labels = c("First","Second", "Third", "Fourth"))
})

# Reordering
df <- df[with(df, order(patient_id, fumo_half)),]  # sort by patient_id and then by fumo

# run models based on intervals for Medicaid_flag
# first interval
df<-df[which(df$interval==int),]
mod<-coxph(Surv(fumo, can_dead) ~ In_Medicaid_Flag + race_ethnicity +age_cat + Yost_ACS_2006_2010_quintile + cluster(state), data = df) 
summary(mod)

# need to get HRs in a dataframe
a<-as.data.frame(exp(cbind(HR = coef(mod), confint(mod))))
  a<-a[c(1),] %>%
   rownames_to_column() %>%
    mutate(model= time,
          Group = cantype) 
}

# Run top three cancer types
a <-cantype("I. Leukemias, myeloproliferative diseases, and myelodysplastic diseases", "First", 0)
b <-cantype("I. Leukemias, myeloproliferative diseases, and myelodysplastic diseases", "Second", 1)
c <-cantype("I. Leukemias, myeloproliferative diseases, and myelodysplastic diseases", "Third", 2)
d <-cantype("I. Leukemias, myeloproliferative diseases, and myelodysplastic diseases", "Fourth", 3)

# Validate function for one cancer type
test <- survSplit(data  = seer0to19 %>% 
                  filter(can_type == "I. Leukemias, myeloproliferative diseases, and myelodysplastic diseases"),
                            cut   = c(12, 24, 36),       # cut at time 12,24,36
                            end   = "fumo_half",    # original survival time
                            event = "can_dead",   # event indicator
                            start = "start")    # will be created. zero by default

# Recoding
test<- within(test, {
    # Create new survival object
    SurvObj <- Surv(start, fumo_half, can_dead) 
    # Create interval indicator
    interval <- factor(start, levels = c(0,12, 24, 36), labels = c("First","Second", "Third", "Fourth"))
})

# Reordering
test <- test[with(test, order(patient_id, fumo_half)),]  # sort by patient_id and then by fumo

# run models based on intervals for Medicaid_flag
# first interval
test <- test[which(test$interval=="First"),]
mod<-coxph(Surv(fumo, can_dead) ~ In_Medicaid_Flag + race_ethnicity +age_cat + Yost_ACS_2006_2010_quintile + cluster(state), data = test) 
summary(mod)

# need to get HRs in a dataframe
a.2<-as.data.frame(exp(cbind(HR = coef(mod), confint(mod))))
  a.2<-a.2[c(1),] %>%
   rownames_to_column() %>%
    mutate(model= 0,
          Group = "I. Leukemias, myeloproliferative diseases, and myelodysplastic diseases")

# Not presented
# e <-cantype("II. Lymphomas and reticuloendothelial neoplasms", "First", 0) # converg. issues
# f <-cantype("II. Lymphomas and reticuloendothelial neoplasms", "Second", 1) # converg. issues
# g <-cantype("II. Lymphomas and reticuloendothelial neoplasms", "Third", 2) # converg. issues
# h <-cantype("II. Lymphomas and reticuloendothelial neoplasms", "Fourth", 3)

i <-cantype("III. CNS and miscellaneous intracranial and intraspinal neoplasms", "First", 0) 
j <-cantype("III. CNS and miscellaneous intracranial and intraspinal neoplasms", "Second", 1)
k <-cantype("III. CNS and miscellaneous intracranial and intraspinal neoplasms", "Third", 2) 
l <-cantype("III. CNS and miscellaneous intracranial and intraspinal neoplasms", "Fourth", 3)

SuppTable6b<-rbind(a,b,c,d,i,j,k,l)

SuppTable6b$model <- factor(SuppTable6b$model, levels = c(0:3), labels = c("0 to 12 months", "12 to 24 months","24 to 36 months", ">36 months"))

table(seer0to19$can_type)
```

# Group by cancer type and plot
```{r}
SuppTable6b %>%
  group_by(Group) %>%
  ggplot() +
  geom_point(aes(y=HR, x=model)) + 
  geom_hline(yintercept =1, linetype=2) +
  theme(axis.text.y=element_blank()) +
  geom_errorbar(aes(y=HR, x=model, ymax = `2.5 %`, ymin = `97.5 %`), width = 0.1) +
  theme_bw() +
  theme(axis.line = element_line(colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank(),
    axis.text.x=element_text(size=11, face = "bold", color = "black"),
    axis.text.y=element_text(size=11, face = "bold", color = "black"),
    axis.title.x=element_text(size=12, face = "bold", color = "black"),
    axis.title.y=element_text(size=12, face = "bold", color = "black"))+
  coord_flip() + 
  facet_wrap(~Group, nrow=4, ncol=2, scales = "free") +
  labs( x = "Time interval") + 
  theme(strip.placement = "inside", legend.position = "bottom",  strip.text = element_text(size = 9, face="bold", color="black"), strip.background = element_rect(fill="lightgray"), plot.title = element_text(face="bold"), legend.text=element_text(size=12, face="bold"))
```

# run models based on intervals for mcont66
```{r}
# first interval
res.cox12m3 <- coxph(Surv(fumo, can_dead) ~ mcont66 + race_ethnicity +age_cat + 
                     Yost_ACS_2006_2010_quintile + cluster(state), data = seer0to19first) 
summary(res.cox12m3)

# second interval
seer0to19second<-seer0to19.cp.format[which(seer0to19.cp.format$interval=="Second"),]
# adjusted models 0 to 19
res.cox24m3 <- coxph(Surv(fumo, can_dead) ~ mcont66 + race_ethnicity +age_cat + 
                     Yost_ACS_2006_2010_quintile + cluster(state), data = seer0to19second) 
summary(res.cox24m3)

# third interval
seer0to19third<-seer0to19.cp.format[which(seer0to19.cp.format$interval=="Third"),]
# adjusted models 0 to 19
res.cox36m3 <- coxph(Surv(fumo, can_dead) ~ mcont66 + race_ethnicity +age_cat + 
                     Yost_ACS_2006_2010_quintile + cluster(state), data = seer0to19third) 
summary(res.cox36m3)

# fourth interval
seer0to19fourth<-seer0to19.cp.format[which(seer0to19.cp.format$interval=="Fourth"),]
# adjusted models 0 to 19
res.cox36plusm3 <- coxph(Surv(fumo, can_dead) ~ mcont66 + race_ethnicity +age_cat + 
                     Yost_ACS_2006_2010_quintile + cluster(state), data = seer0to19fourth) 
summary(res.cox36plusm3)
```

# SUPPLEMETARY TABLE 6c: Graph hazard ratios and confidence intervals across time for mcont66 variable
```{r}
# need to get HRs in a dataframe
a<-as.data.frame(exp(cbind(HR = coef(res.cox12m3), confint(res.cox12m3))))
   a<-a[c(1,2,3),] %>%
    rownames_to_column() %>%
    mutate(model= 0) %>%
    mutate(Group = "Overall")

b<-as.data.frame(exp(cbind(HR = coef(res.cox24m3), confint(res.cox24m3))))
   b<-b[c(1,2,3),] %>%
    rownames_to_column() %>%
    mutate(model= 1)  %>%
    mutate(Group ="Overall")

c<-as.data.frame(exp(cbind(HR = coef(res.cox36m3), confint(res.cox36m3))))
   c<-c[c(1,2,3),] %>%
    rownames_to_column() %>%
    mutate(model= 2)  %>%
    mutate(Group ="Overall")

d <-as.data.frame(exp(cbind(HR = coef(res.cox36plusm3), confint(res.cox36plusm3))))
   d<-d[c(1,2,3),] %>%
    rownames_to_column() %>%
    mutate(model=3)  %>%
    mutate(Group ="Overall")

SuppTable6c<- rbind(a,b,c,d)

SuppTable6c$model <- factor(SuppTable6c$model, levels = c(0:3), labels = c("0 to 12 months", "12 to 24 months","24 to 36 months", ">36 months"))

# graph HRs and 95% CIs
SuppTable6c %>%
  ggplot() +
  geom_point(aes(y=HR, x=model)) + 
  geom_hline(yintercept =1, linetype=2) +
  theme(axis.text.y=element_blank()) +
  geom_errorbar(aes(y=HR, x=model, ymax = `2.5 %`, ymin = `97.5 %`), width = 0.1) +
  theme_bw() +
  theme(axis.line = element_line(colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank(),
    axis.text.x=element_text(size=11, face = "bold", color = "black"),
    axis.text.y=element_text(size=11, face = "bold", color = "black"),
    axis.title.x=element_text(size=12, face = "bold", color = "black"),
    axis.title.y=element_text(size=12, face = "bold", color = "black"))+
  coord_flip() +
 facet_wrap(~rowname, nrow=1, ncol=3) +
  labs(title = "Category", x = "time") + 
  theme(strip.placement = "inside", legend.position = "bottom",  strip.text = element_text(size = 9, face="bold", color="black"), strip.background = element_rect(fill="lightgray"), plot.title = element_text(face="bold"), legend.text=element_text(size=9, face="bold"))
```
# SUPPLEMENTARY TABLE 6: HRs by time interval
```{r}
SuppTable6 <- rbind(SuppTable6a, SuppTable6b, SuppTable6c)
```

@@

# 6
SuppTable6 <- SuppTable6 %>%
  rename(`Time interval` = model,
         Category = rowname,
         `lower 95% CI` = `2.5 %`,
         `upper 95% CI` = `97.5 %`) %>%
  mutate(Category = case_when(Category == "In_Medicaid_FlagEnrolled" ~ "Enrolled",
            Category == "mcont66Discontinuous" ~ "Discontinuous",
            Category == "mcont66Other" ~ "Other",
            Category == "mcont66Continuous" ~ "Continuous")) %>%

  mutate_if(is.numeric, round, 2)

SuppTable6$`HR (95% CI)` <-paste0(SuppTable6$HR, " (", SuppTable6$`lower 95% CI`, " to ", SuppTable6$`upper 95% CI`, ")") 
SuppTable6 <- SuppTable6 %>%
  dplyr::select(1,5,6,7)

@@

# Export supplementary tables to excel
```{r}
sheets <- list("Supp Table 1 (stage cantype)" = SuppTable1,
               "Supp Table 2 (surv overall)" = SuppTable2,
               "Supp Table 3 (surv prob age )" = SuppTable3,
               "Supp Table 4 (surv prob race )" = SuppTable4,
               "Supp Table 5 (surv prob can )" = SuppTable5,
               "Supp Table 6 (ph analysis)" = SuppTable6, 
               "Supp Table 7 (EM)" = SuppTable7)
write.xlsx(sheets, file="Supplementary tables.xlsx", showNA=TRUE, overwrite = TRUE)
```

>>>>

# Supplementary Table 6a: Run models based on intervals for Medicaid_flag
```{r}
age <- unique(seer0to19.cp.format$age_cat)

# testing here
m <-coxph(SurvObj ~ In_Medicaid_Flag + In_Medicaid_Flag*strata(interval) + race_ethnicity + age_cat + Yost_ACS_2006_2010_quintile + cluster(state), seer0to19.cp.format)

m
library(multcomp)
X<- matrix(c(1,0,0,0,0,0,0,0,0,0,0,0,0,0,0), 1)

t <- glht(m, linfct = X) 
summary(t) # here are the results

CI <- confint(t)
CI <- as.data.frame(exp(CI$confint))
# end testing

W <- matrix(c(1,0,0,0,0,0,0,0,0,0,0,0,0,0,0), 1) 
X <- matrix(c(1,0,0,0,0,0,0,0,0,0,0,0,1,0,0), 1)
Y <- matrix(c(1,0,0,0,0,0,0,0,0,0,0,0,0,1,0), 1)
Z <- matrix(c(1,0,0,0,0,0,0,0,0,0,0,0,0,0,1), 1)

x <- coxph(SurvObj ~ In_Medicaid_Flag + In_Medicaid_Flag*strata(interval) + race_ethnicity + age_cat + Yost_ACS_2006_2010_quintile + cluster(state), data = seer0to19.cp.format) 
  t0<- glht(x, linfct = W) 
  df1<-confint(t0)
  df1 <- as.data.frame(exp(df1$confint))

  df1$interval = "0-<12" # enrolled first interval

  t12<- glht(x, linfct = X) 
  df2<-confint(t12)
  df2 <- as.data.frame(exp(df2$confint))
  df2$interval = "12-<24" # enrolled second interval

  t24<- glht(x, linfct = Y) 
  df3<-confint(t24)
  df3 <- as.data.frame(exp(df3$confint))
  df3$interval = "24-<36" # enrolled third interval

  t36 <- glht(x, linfct = Z) 
  df4 <-confint(t36)
  df4 <- as.data.frame(exp(df4$confint))
  df4$interval = "36+" # enrolled fourth interval

  results <-rbind(df1, df2, df3, df4)  # this puts the results from each loop round in the results data file

  results$Group <- "Overall"
  results$category <- "Enrolled"
SuppTable6a <- results

@@

# Graph hazard ratios and confidence intervals across time for enrolled variable
```{r}
p<- results %>%
  ggplot() +
  geom_point(aes(y=Estimate, x= interval), na.rm=TRUE, position=position_dodge(width=0.9), size =4) + 
  geom_hline(yintercept =1, linetype=2) +
  theme(axis.text.y=element_blank()) +
  geom_errorbar(aes(y=Estimate, x=interval, ymax = lwr, ymin = upr), na.rm=TRUE, position=position_dodge(width=0.9), width = 0.1) +
  theme_bw() +
  theme(axis.line = element_line(colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank(),
    axis.text.x=element_text(size=11, face = "bold", color = "black"),
    axis.text.y=element_text(size=11, face = "bold", color = "black"),
    axis.title.x=element_text(size=12, face = "bold", color = "black"),
    axis.title.y=element_text(size=12, face = "bold", color = "black"))+
  coord_flip() 
p
```
# SUPPLEMENTARY TABLE 6b: Which cancer is driving this? 
```{r}
# In_Medicaid_Flag
results <- data.frame(matrix(ncol=5, nrow=0)) # create empty table for results that will be populated by for loop
columns<-c("estimate", "lwr", "upr", "age", "interval") # label the columns with names
colnames(results) <- columns

cantype <- c("I. Leukemias, myeloproliferative diseases, and myelodysplastic diseases", "III. CNS and miscellaneous intracranial and intraspinal neoplasms")
colnames(seer0to19.cp.format)

for (i in cantype) {
  df <- seer0to19.cp.format %>% filter(can_type == i)

  x <- coxph(SurvObj ~ In_Medicaid_Flag + In_Medicaid_Flag*strata(interval) + age_cat + race_ethnicity + Yost_ACS_2006_2010_quintile + cluster(state), data = df) 
  t0<- glht(x, linfct = W) 
  df1<-confint(t0)
  df1 <- as.data.frame(exp(df1$confint))
  df1$Group <- i
  df1$interval = "0-<12" # enrolled first interval

  t12<- glht(x, linfct = X) 
  df2<-confint(t12)
  df2 <- as.data.frame(exp(df2$confint))
  df2$Group <- i
  df2$interval = "12-<24" # enrolled second interval

  t24<- glht(x, linfct = Y) 
  df3<-confint(t24)
  df3 <- as.data.frame(exp(df3$confint))
  df3$Group <- i
  df3$interval = "24-<36" # enrolled third interval

  t36 <- glht(x, linfct = Z) 
  df4 <-confint(t36)
  df4 <- as.data.frame(exp(df4$confint))
  df4$Group <- i
  df4$interval = "36+" # enrolled fourth interval

  results <-rbind(results, df1, df2, df3, df4)  # this puts the results from each loop round in the results data file
}

results$category = "Enrolled"
SuppTable6b <- results
```

# Group by cancer type and plot
```{r}
SuppTable6b %>%
  group_by(Group) %>%
  ggplot() +
  geom_point(aes(y=Estimate, x=interval)) + 
  geom_hline(yintercept =1, linetype=2) +
  theme(axis.text.y=element_blank()) +
  geom_errorbar(aes(y=Estimate, x=interval, ymax = lwr, ymin = upr), width = 0.1) +
  theme_bw() +
  theme(axis.line = element_line(colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank(),
    axis.text.x=element_text(size=11, face = "bold", color = "black"),
    axis.text.y=element_text(size=11, face = "bold", color = "black"),
    axis.title.x=element_text(size=12, face = "bold", color = "black"),
    axis.title.y=element_text(size=12, face = "bold", color = "black"))+
  coord_flip() + 
  facet_wrap(~Group, nrow=4, ncol=2, scales = "free") +
  labs( x = "Time interval") + 
  theme(strip.placement = "inside", legend.position = "bottom",  strip.text = element_text(size = 9, face="bold", color="black"), strip.background = element_rect(fill="lightgray"), plot.title = element_text(face="bold"), legend.text=element_text(size=12, face="bold"))
```
# run models based on intervals for mcont66
```{r}
# testing here
m <-coxph(SurvObj ~ mcont66 + mcont66*strata(interval) + age_cat + race_ethnicity +  Yost_ACS_2006_2010_quintile + cluster(state), data = seer0to19.cp.format) 
m

X <- matrix(c(0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0), 1)

t <- glht(m, linfct = X) 
summary(t) # here are the results

CI<-confint(t)
CI <- as.data.frame(exp(CI$confint))
# end testing

A <- matrix(c(1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0), 1) # discontinuous 1st interval
B <- matrix(c(0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0), 1) # other 1st interval
C <- matrix(c(0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0), 1) # Not enrolled 1st interval

D <- matrix(c(1,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0), 1) # discontinuous 2nd interval
E <- matrix(c(0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0), 1) # other 2nd interval
F <- matrix(c(0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0), 1) # Not enrolled 2nd interval

G <- matrix(c(1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0), 1) # discontinuous 3rd interval
H <- matrix(c(0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0), 1) # other 3rd interval
I <- matrix(c(0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0), 1) # Not enrolled 3rd interval

J <- matrix(c(1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0), 1) # discontinuous 3rd interval
K <- matrix(c(0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0), 1) # other 3rd interval
L <- matrix(c(0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1), 1) # Not enrolled 3rd interval

  x <- coxph(SurvObj ~ mcont66 + mcont66*strata(interval) + race_ethnicity + age_cat + Yost_ACS_2006_2010_quintile + cluster(state), data = seer0to19.cp.format) 
  t0<- glht(x, linfct = A) 
  df1<-confint(t0)
  df1 <- as.data.frame(exp(df1$confint))
  df1$Group <- "Overall"
  df1$interval = "0-<12"
  df1$category ="continuous" # first interval

  t0<- glht(x, linfct = B) 
  df2<-confint(t0)
  df2 <- as.data.frame(exp(df2$confint))
  df2$Group <- "Overall"
  df2$interval = "0-<12"
  df2$category ="discontinuous" # first interval

  t0<- glht(x, linfct = C) 
  df3<-confint(t0)
  df3 <- as.data.frame(exp(df3$confint))
  df3$Group <- "Overall"
  df3$interval = "0-<12"
  df3$category ="other" # first interval

  t12<- glht(x, linfct = D) 
  df4<-confint(t12)
  df4 <- as.data.frame(exp(df4$confint))
  df4$Group <- "Overall"
  df4$interval = "12-<24"
  df4$category ="continuous" # second interval

  t12<- glht(x, linfct = E) 
  df5<-confint(t12)
  df5 <- as.data.frame(exp(df5$confint))
  df5$Group <- "Overall"
  df5$interval = "12-<24"
  df5$category ="discontinuous" # second interval

  t12<- glht(x, linfct = F) 
  df6<-confint(t12)
  df6 <- as.data.frame(exp(df6$confint))
  df6$Group <- "Overall"
  df6$interval = "12-<24"
  df6$category ="other" # second interval

  t24<- glht(x, linfct = G) 
  df7<-confint(t24)
  df7 <- as.data.frame(exp(df7$confint))
  df7$Group <- "Overall"
  df7$interval = "24-<36"
  df7$category ="continuous" # third interval

  t24<- glht(x, linfct = H) 
  df8<-confint(t24)
  df8<- as.data.frame(exp(df8$confint))
  df8$Group <- "Overall"
  df8$interval = "24-<36"
  df8$category ="discontinuous" # third interval

  t24<- glht(x, linfct = I) 
  df9<-confint(t24)
  df9 <- as.data.frame(exp(df9$confint))
  df9$Group <- "Overall"
  df9$interval = "24-<36"
  df9$category ="other" # third interval

  t36<- glht(x, linfct = J) 
  df10<-confint(t36)
  df10 <- as.data.frame(exp(df10$confint))
  df10$Group <- "Overall"
  df10$interval = "36+"
  df10$category ="continuous" # fourth interval

  t36<- glht(x, linfct = K) 
  df11<-confint(t36)
  df11<- as.data.frame(exp(df11$confint))
  df11$Group <- "Overall"
  df11$interval = "36+"
  df11$category ="discontinuous" # fourth interval

  t36<- glht(x, linfct = L) 
  df12<-confint(t36)
  df12 <- as.data.frame(exp(df12$confint))
  df12$Group <- "Overall"
  df12$interval = "36+"
  df12$category ="other" # fourth interval

  results <-rbind(df1, df2, df3, df4, df5, df6, df7, df8, df9, df10, df11, df12)  # this puts the results from each loop round in the results data file

SuppTable6c <- results
```

# SUPPLEMETARY TABLE 6c: Graph hazard ratios and confidence intervals across time for mcont66 variable
```{r}
# graph HRs and 95% CIs
SuppTable6c %>%
  ggplot() +
  geom_point(aes(y=Estimate, x=interval, group = category, color = category),  position=position_dodge(width=0.9)) + 
  geom_hline(yintercept =1, linetype=2) +
  theme(axis.text.y=element_blank()) +
  geom_errorbar(aes(y=Estimate, x=interval, ymax = lwr, ymin = upr,  group = category, color = category), position=position_dodge(width=0.9), width = 0.1) +
  geom_vline(xintercept =c(1.5, 2.5,3.5,4.5,5.5,6.5,7.5,8.5,9.5), linetype=2, color = "lightgray") +
  theme_bw() +
  theme(axis.line = element_line(colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank(),
    axis.text.x=element_text(size=11, face = "bold", color = "black"),
    axis.text.y=element_text(size=11, face = "bold", color = "black"),
    axis.title.x=element_text(size=12, face = "bold", color = "black"),
    axis.title.y=element_text(size=12, face = "bold", color = "black"))+
  coord_flip() +
  labs(y = "HR", x = "Interval") + 
  theme(strip.placement = "inside", legend.position = "bottom",  strip.text = element_text(size = 9, face="bold", color="black"), strip.background = element_rect(fill="lightgray"), plot.title = element_text(face="bold"), legend.text=element_text(size=9, face="bold"))
```

# SUPPLEMENTARY TABLE 6: HRs by time interval
```{r}
SuppTable6 <- rbind(SuppTable6a, SuppTable6b, SuppTable6c)

@@

# 6
SuppTable6 <- SuppTable6 %>%
  rename(`Time interval` = interval,
         Category = category,
         `lower 95% CI` = lwr,
         `upper 95% CI` = upr) %>%
  mutate(Category = case_when(Category == "Enrolled"~ "Enrolled",
            Category == "discontinuous" ~ "Discontinuous",
            Category == "other" ~ "Other",
            Category == "continuous" ~ "Continuous")) %>%
  mutate_if(is.numeric, round, 2)

SuppTable6$`HR (95% CI)` <-paste0(SuppTable6$Estimate, " (", SuppTable6$`lower 95% CI`, " to ", SuppTable6$`upper 95% CI`, ")") 
SuppTable6 <- SuppTable6 %>%
  dplyr::select(4,5,6,7)

@@

# Export supplementary tables to excel
```{r}
sheets <- list("Supp Table 1 (stage cantype)" = SuppTable1,
               "Supp Table 2 (surv overall)" = SuppTable2,
               "Supp Table 3 (surv prob age )" = SuppTable3,
               "Supp Table 4 (surv prob race )" = SuppTable4,
               "Supp Table 5 (surv prob can )" = SuppTable5,
               "Supp Table 6 (ph analysis)" = SuppTable6, 
               "Supp Table 7 (EM)" = SuppTable7)
write.xlsx(sheets, file="Supplementary tables updated.xlsx", showNA=TRUE, overwrite = TRUE)
```
